Covariance as constraint: Leveraging leaf economic relationships to constrain plant functional type trait estimates

### 2018-01-08 manuscript-md/02_methods.Rmd
Add intercept analysis to methods

If all three models performed equally well at all sample sizes, their respective slope coefficients would be statistically indistinguishable.
On the other hand, models that perform better should have lower slope ($b_1$) coefficients, indicating a slower increase in the uncertainty ($\alpha$) with decreasing sample size ($n$).

>>>>

If all three models performed equally well at all sample sizes, their respective slope and intercept coefficients would be statistically indistinguishable.
On the other hand, models that perform better should have
lower intercept ($b_0$) coefficients, indicating generally lower uncertainty,
and
lower slope ($b_1$) coefficients, indicating a reduced sensitivity of uncertainty ($\alpha$) to sample size ($n$).
